Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2014-01-31 paper/paper.tex
Added reference

Another successful approach to program synthesis has been \emph{program
sketching}, in particular the {\sc sketch} tool~\cite{lezama-thesis,sketch}.  This method
requires the programmer to provide a \emph{program sketch}, written in a
C-like language, together with either a specification (written in the same
language) or a suite of unit tests.  The sketch is a skeleton program
containing much of the high-level structure of the final program, but with
several ``holes'', which {\sc sketch} fills in to meet the specification.
Despite the many similarities, our problem domains are quite different:
sketching is able to make use of human insight to synthesise fairly large
programs, whereas we are optimised for synthesising small (but intricate)
programs without guidance.

@@

\paragraph{Acknowledgements}
We thank Martin Brain for his insight and advice during our synthesis discussions.

>>>>

Another successful approach to program synthesis has been \emph{program
sketching}, in particular the {\sc sketch} tool~\cite{lezama-thesis,sketch}.  This method
requires the programmer to provide a \emph{program sketch}, written in a
C-like language, together with either a specification (written in the same
language) or a suite of unit tests.  The sketch is a skeleton program
containing much of the high-level structure of the final program, but with
several ``holes'', which {\sc sketch} fills in to meet the specification.
Despite the many similarities, our problem domains are quite different:
sketching is able to make use of human insight to synthesise fairly large
programs, whereas we are optimised for synthesising small (but intricate)
programs without guidance.  A sketching-like approach to optimising
fixed point arithmetic code was described in~\cite{eldib-wang}.  This
work is similar in goal to our floating-point work, but is more restricted
in scope in that it only tries to minimise register widths for embedded
systems using fixed point arithmetic.

@@

\paragraph{Acknowledgements}
We thank Martin Brain for his insight and advice during our synthesis discussions.
Also, thanks to Cristina David for her extensive help and proof reading during the
preparation of this paper.
